CLT Results

### 2022-04-19 analysis/clt_data_processing.Rmd
add more data

data_zas <- proc_data_zas%>%
  left_join(aoa)%>%
  select(-timestamp)%>%
  ungroup()%>%
  mutate(age_group = substr(age,0,1))%>%
  select(-bday, -test_day)%>%
  filter(!is.na(age))%>%
  mutate(correct = ifelse(targetWord == chosenWord, 1,0))%>%
  mutate(targetWord = ifelse(targetWord == "kangoroo", "kangaroo", targetWord))%>%
  left_join(aoa)%>%
  ungroup()

@@

```{r}
# reminder1 <- read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 15)
# 
# bind_rows(
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 1),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 2),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 3),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 4),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 5),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 7),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 10),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 12)
#   )%>%
#   filter(!code %in% data$subjID)%>%
#   filter(!code %in% reminder1$code)%>%
#   filter(code != "RY5sK3xF")%>%
#   filter(code != "s6fdepZJ")%>%
#   write_xlsx("../data/clt_reminder2.xlsx")
```

@@

ggplot(p1_2, aes(x = mean_orderA, y = mean_orderB))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r")+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = .75)+
  #geom_textpath(aes(label = german), hjust = -.2) +
  #geom_hline(yintercept = 0.25, alpha = .5)+
  #geom_vline(xintercept = 0.25, alpha = .5)+
  geom_errorbar(aes(xmin = ci_lower_orderA, xmax = ci_upper_orderA), alpha = .5)+
  geom_errorbar(aes(ymin = ci_lower_orderB, ymax = ci_upper_orderB), alpha = .5)+
  geom_point( size =2, stroke = 1, alpha= .75)+
  labs(x = "Order A", y = "Order B")+
  ylim(0,1)+
  xlim(0,1)+
  theme_minimal()
```

>>>>

data_zas <- proc_data_zas%>%
  left_join(aoa)%>%
  select(-timestamp)%>%
  ungroup()%>%
  mutate(age_group = substr(age,0,1))%>%
  select(-bday, -test_day)%>%
  filter(!is.na(age))%>%
  mutate(correct = ifelse(targetWord == chosenWord, 1,0))%>%
  mutate(targetWord = ifelse(targetWord == "kangoroo", "kangaroo", targetWord))%>%
  left_join(aoa)%>%
  ungroup()%>%
  filter(age_group < 9)

@@

```{r}
# reminder1 <- read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 15)
# reminder2 <- read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 16)
# 
# bind_rows(
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 1),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 2),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 3),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 4),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 5),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 7),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 10),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 11),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 12),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 13),
#   read_xlsx("../../../../Cloud/Shared/CLT_Kinderlisten_fuer_Emailversandt_14032022.xlsx", sheet = 14)
#   )%>%
#   filter(!code %in% data$subjID)%>%
#   filter(!code %in% reminder1$code)%>%
#   filter(!code %in% reminder2$code)%>%
#   filter(code != "RY5sK3xF")%>%
#   filter(code != "s6fdepZJ")%>%
#   write_xlsx("../data/clt_reminder3.xlsx")
```

@@

ggplot(p1_2, aes(x = mean_orderA, y = mean_orderB))+
  stat_cor(aes(label = paste(..r.label..)),r.accuracy = 0.01, cor.coef.name = "r")+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = .75)+
  geom_textpath(aes(label = german), hjust = -.2) +
  #geom_hline(yintercept = 0.25, alpha = .5)+
  #geom_vline(xintercept = 0.25, alpha = .5)+
  geom_errorbar(aes(xmin = ci_lower_orderA, xmax = ci_upper_orderA), alpha = .5)+
  geom_errorbar(aes(ymin = ci_lower_orderB, ymax = ci_upper_orderB), alpha = .5)+
  geom_point( size =2, stroke = 1, alpha= .75)+
  labs(x = "Order A", y = "Order B")+
  ylim(0,1)+
  xlim(0,1)+
  theme_minimal()
```
